---
title: "HongKongAirbnb"
author: "Yonkee ZHENG"
output: html_document
---

# Mining of HK Airbnb data
Data from http://insideairbnb.com/get-the-data
```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(leaflet)
```

```{r}
listing = read.csv('HongKongAirbnb.csv')
head(listing)
```

Change the data type of last_review to Date in order to visualize easier later.
```{r}
listing$last_review = as.Date.character(listing$last_review)
head(listing)
```

Check whether price and minimum night are non-negative.
And to get the minimum total money, I multiply price and minimum_nights.
```{r}
table(listing$price <= 0)
table(listing$minimum_nights<=0)
listing$minimum_total_money = listing$price * listing$minimum_nights
```

Select the data where price is non-negative.
```{r}
listing1 = listing[!(listing$price<=0),]
head(listing1)
```

```{r}
summary(listing1)
```

The most important variable is price.
Hence, I want to see the overall distribution of price.
```{r}
ggplot(listing1, aes(price)) +
  geom_density(alpha = 0.5, fill = "blue") +
  ggtitle("Distribution of price") +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(xintercept = mean(listing1$price), size = 0.5, linetype = 2)
```

Since the distribution is very skewed, it's better to use log transformation to gain a better insight.
```{r}
ggplot(listing1, aes(price)) +
  geom_density(alpha = 0.5, fill = "blue") +
  ggtitle("Log transformed distribution of price",
          subtitle = expression("With" ~'log'[10] ~ "transformation of x-axis")) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.title = element_text()) +
  geom_vline(xintercept = mean(listing1$price), size = 0.5, linetype = 2) +
  scale_x_log10()
```

Average Price of each Neighbourhood
```{r}
nbh.price = listing1 %>% group_by(neighbourhood_cleansed) %>% 
  summarise(mean_price = mean(price)) %>% arrange(desc(mean_price))
ggplot(nbh.price, aes(x = reorder(neighbourhood_cleansed, -mean_price), y = mean_price)) + 
  geom_bar(stat="identity") + 
  labs(title="Average Price of Rooms in each Neighbourhood") + 
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90)) + 
  xlab("") + ylab("Mean Price") +
  geom_text(aes(label = round(mean_price,0)),vjust=-0.2, size=3)
```

The log transformed distribution of each neighbourhood.
```{r}
ggplot(listing1, aes(price)) +
  geom_density(alpha = 0.5, fill = "blue") +
  ggtitle("Log transformed distribution of price by neighbourhood",
          subtitle = expression("With" ~'log'[10] ~ "transformation of x-axis")) +
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 7), axis.text.x = element_text(size = 7)) + 
  geom_vline(data = nbh.price, aes(xintercept = mean_price), size = 0.2, linetype = 2) +
  facet_wrap(~neighbourhood_cleansed) +
  scale_x_log10() +
  geom_text(data = nbh.price, y = 2, size = 2.5,
            aes(x = mean_price, label = round(mean_price,0)))
```

Then analyze the price of rooms by different room types.
```{r}
ggplot(listing1, aes(x = room_type, y = price)) +
  geom_boxplot(aes(fill = room_type)) + 
  scale_y_log10() +
  xlab("Room type") + ylab("Price") +
  ggtitle("Boxplots of price by room types") +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_hline(yintercept = mean(listing1$price), linetype = 2)
```

The entire home or apartment has the highest average price, while shared room has the lowest average price.

Also analyze the minimum total price of each room type.
```{r}
ggplot(listing1, aes(x = room_type, y = minimum_total_money)) +
  geom_boxplot(aes(fill = room_type)) + 
  scale_y_log10() +
  xlab("Room type") + ylab("Minimum total price") +
  ggtitle("Boxplots of minimum total price by room types") +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_hline(yintercept = mean(listing1$minimum_total_money), linetype = 2)
```

The entire home or apartment has the highest average minimum total price. Surprisingly, hotel room has the lowest average minimum total price.

Comparison of mean price of each neighbourhood and room types.
```{r}
nbh.rt.price <- listing1 %>% group_by(neighbourhood_cleansed, room_type) %>% 
  summarise(mean_price = mean(price))
ggplot(nbh.rt.price, aes(x = reorder(neighbourhood_cleansed, -mean_price), 
                         y = mean_price, fill = room_type)) + 
  geom_bar(stat="identity",colour="black",position=position_dodge()) + 
  labs(title="Comparison of mean price of each neighbourhood by different room types") + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 90),
        legend.position = c(0.9, 0.7), legend.title.align = 0.5) + 
  xlab("") + ylab("Mean price") +
  scale_fill_discrete(name = 'Room Type')
```

Find the relationship between the price and availability in a year.
```{r}
ggplot(listing1, aes(availability_365, price)) +
  geom_point(alpha = 0.5, color = 'blue') +
  xlab("Availability during year") + ylab("Price") +
  ggtitle("Relationship between price and availability during a year",
          subtitle = expression("With" ~'log'[10] ~ "transformation of y-axis")) +
  theme(plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5)) +
  scale_y_log10()
```

There is not a clear pattern in this figure and hence no relationship between price and availability during a year.

Find the relationship between minimum total money and number of reviews.
```{r}
ggplot(listing1, aes(minimum_total_money, number_of_reviews)) +
  geom_point() + 
  xlab('Minimum total money') +  ylab("Number of reviews") + 
  ggtitle("Relationship between price and number of reviews",
          subtitle = expression("With" ~'log'[10] ~ "transformation of y-axis")) +
  theme(plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5)) +
  scale_x_log10() 
```

Find the relationship between the price and host response time.
```{r}
listing2 = listing1 %>% drop_na(host_response_rate)
listing2$host_response_time_reorder = factor(listing2$host_response_time,
  levels = c('within an hour', 'within a few hours','within a day','a few days or more'))
ggplot(listing2, aes(x = host_response_time_reorder, y = price)) +
  geom_boxplot(aes(fill = host_response_time)) + 
  scale_y_log10() +
  xlab("Host response time") + ylab("Price") +
  ggtitle("Boxplots of price by host response time") +
  theme(plot.title = element_text(hjust = 0.5))
```

Relationship between price and accommodates.
```{r}
ggplot(listing1, aes(x = accommodates, y = price)) +
  geom_point() + 
  geom_smooth() +
  scale_y_log10() +
  xlab("Accommodates") + ylab("Price") +
  ggtitle("Relationship between price and accommodates") +
  theme(plot.title = element_text(hjust = 0.5))
```

Number of rooms by neighbourhood.
```{r}
nbh.count = listing1 %>% group_by(neighbourhood_cleansed) %>% 
  summarise(count = n()) %>% arrange(desc(count))
ggplot(nbh.count, aes(x = reorder(neighbourhood_cleansed, -count), y = count)) + 
  geom_bar(stat="identity") + 
  labs(title="Number of rooms by neighbourhood") + 
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90)) + 
  xlab("") + 
  geom_text(aes(label = count), vjust=-0.2, size=3)
```

Relationships between host response rate and review scores value.
```{r}
ggplot(listing1,aes(host_response_rate, review_scores_value)) +
  geom_point() +
  geom_smooth() +
  ggtitle('Relationships between host response rate and review scores value') +
  xlab('Host response rate') + ylab('Review scores value') +
  theme(plot.title = element_text(hjust = 0.5))
```

Relationship between host acceptance rate and review scores value.
```{r}
ggplot(listing1,aes(host_acceptance_rate, review_scores_value)) +
  geom_point() +
  geom_smooth() +
  ggtitle('Relationships between host response rate and review scores value') +
  xlab('Host acceptance rate') + ylab('Review scores value') +
  theme(plot.title = element_text(hjust = 0.5))
```

Leaflet map
```{r}
pal = colorFactor(palette = "plasma",
                  listing1$neighbourhood_cleansed)
leaflet(data = listing1) %>% addProviderTiles(providers$CartoDB.DarkMatterNoLabels) %>%
  addCircleMarkers(~longitude, ~latitude, color = ~pal(neighbourhood_cleansed), 
                   weight = 1, radius=1, fillOpacity = 0.1, opacity = 0.1,
                   label = paste("ID:", listing1$id)) %>% 
     addLegend("bottomright", pal = pal, values = ~neighbourhood_cleansed,
     title = "Neighbourhood",
     opacity = 1)
```